\Title

### 2020-02-18 manuscript/manuscript.tex
Improve figure captions

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block averaged sources. (a) Given a set of observation points (b) we divide
        the survey region on blocks of equal size and compute the median
        location of the observation points that fall inside each block.
        (c) A source point is located beneath each block averaged coordinate.
        The number of point sources could be less or equal to the number of
        observation points.
        No source is located beneath unpopulated blocks.
    }
    \label{fig:block-median-sources}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block averaged sources.
        (a)~Given a set of observation points
        (b)~we divide the survey region on blocks of equal size and compute the
            median location of the observation points that fall inside each
            block.
        (c)~A source point is located beneath each block averaged coordinate.
            The number of point sources could be less or equal to the number of
            observation points. No source is located beneath unpopulated
            blocks.
    }
    \label{fig:block-median-sources}
\end{figure*}
